Intended Table of Contents Thesis

### 2013-03-14 Chapters/Chapter1.tex
Work on lit review non parametric clustering

% Chapter 1

@@

\input{./Chapters/Chapter1/literature_review}

>>>>

% Chapter 1
% !TEX root = ../main.tex

@@

\section{Literature review}
This section will provide a literature review per coherent subject of this thesis.
In subsection \ref{sec:lit_review_segmentation} the research in segmentation and classification of human activities will be discussed.
Subsection \ref{sec:lit_review_nonparametric} will take a look on applied non-parametric methods in clustering (time series) of data.

\input{./Chapters/Chapter1/literature_review_segmentation_and_classification}

\input{./Chapters/Chapter1/literature_review_nonparametric_clustering}

\input{./Chapters/Chapter1/paper_list}
